### 2013-09-17 main.tex
second page with advisor / reader, fix page numbering
working on conclusions

\documentclass[12pt,toc=bibnumbered, a4paper,twoside,DIV=11]{scrbook}
%\documentclass[12pt,toc=bibnumbered, a4paper,twoside]{book}

@@

\begin{center}
\Large\sffamily
\vspace*{1cm}
\textbf{{\huge Learning Structured Prediction For Semantic Image Segmentation}}\\[5mm]
Dissertation\\%[3mm]
zur\\%[3mm]
Erlangung des Doktorgrades (Dr.\ rer.\ nat.)\\%[3mm]
der\\%[3mm]
Mathematisch-Naturwissenschaftlichen Fakult\"at\\%[3mm]
der\\%[3mm]
Rheinischen Friedrich-Wilhelm Universit\"at Bonn\\%[3mm]
vorgelegt von\\%[5mm]
{\LARGE Andreas Christian M\"uller}\\%[5mm]
aus\\%[3mm]
Offenbach am Main\\%[10mm]
Bonn, September 2013
\end{center}
\end{titlepage}

\pagenumbering{Roman}

\tableofcontents
\end{spacing}
%\listoffigures
%\listoftables
\chapter*{Zusammenfassung}
Automatische Segementierung und Erkennung von semantischen Klassen in
natuerlichen Bildern ist ein wichtiges offenes Problem des machinellen Sehens.
Einer der am weitest verbreiteten Ans\"atze zu dieser Aufgabe basiert auf
Conditional Random Fields und Verfahren der strukturierten Vorhersage. Die
Vorhersage f\"ur Modelle zur Bild-Markierung mittels Conditional Random Fields
ist f\"ur gew\"ohnlich nur approiximativ moeglich, bedingt d\"urch das
Vorhandensein von Kreisen in den zugrunde liegenden Nachbarschaftsgraphen.
Aus diesem Grund, und trotz der Beliebtheit von Conditional Random Field
Verfahren, ist das strukturierte Lernen f\"ur solche Anwendungen schlecht
verstanden.
%
Wir untersuchen verschiedene Lernalgorithmen in diesem
Zusammenhang. Wir zeigen, dass es m\"oglich ist trotz des Vorhandenseins von
Kreisen in den Nachbarschaftsgraphen exakte strukturierte Modelle zu lernen.
Wir stellen ausserdem eine Software-Bibliothek vor, die es erlaubt einen
weitreichenden Vergleich der besten Lernverfahren f\"ur strukturiertes Lernen
durchzuf\"uhren.
Unsere Studie erlaubt uns eine Charakterisation der betrachteten Algorithmen
in einer Reihe von Anwendungen, insbesondere der semantischen Segmentierung und
Objektklassensegmentierung.

@@

\pagenumbering{arabic}

@@

\chapter{Conclusion}

>>>>

\documentclass[12pt,toc=bibnumbered, a4paper,twoside,DIV=11,BCOR=.5cm]{scrbook}
%\documentclass[12pt,toc=bibnumbered, a4paper,twoside]{book}

@@

\begin{center}
\Large\sffamily
\vspace*{1cm}
\textbf{{\huge Learning Structured Prediction For Semantic Image Segmentation}}\\[5mm]
Dissertation\\%[3mm]
zur\\%[3mm]
Erlangung des Doktorgrades (Dr.\ rer.\ nat.)\\%[3mm]
der\\%[3mm]
Mathematisch-Naturwissenschaftlichen Fakult\"at\\%[3mm]
der\\%[3mm]
Rheinischen Friedrich-Wilhelm Universit\"at Bonn\\%[3mm]
vorgelegt von\\%[5mm]
{\LARGE Andreas Christian M\"uller}\\%[5mm]
aus\\%[3mm]
Offenbach am Main\\%[10mm]
Bonn, September 2013
\end{center}
\end{titlepage}
%
\thispagestyle{empty}
\vspace*{5cm}
\Large\sffamily
\begin{center}
Angefertigt mit Genehmigung\\
der Mathematisch-Naturwissenschaftlichen Fakult\"at\\
der Rheinischen Friedrich-Wilhelms-Universit\"at Bonn\\
\end{center}
1. Gutachter Prof. Dr. Sven Behnke\\
2. Gutachter Prof. Dr. Reinhard Klein\\
Tag der Promotion:\\
Erscheinungsjahr: 2013\\
\end{spacing}
\pagenumbering{Roman}
\tableofcontents
%\listoffigures
%\listoftables
\chapter*{Zusammenfassung}
Automatische Segementierung und Erkennung von semantischen Klassen in
natuerlichen Bildern ist ein wichtiges offenes Problem des machinellen Sehens.
Einer der am weitest verbreiteten Ans\"atze zu dieser Aufgabe basiert auf
Conditional Random Fields und Verfahren der strukturierten Vorhersage. Die
Vorhersage f\"ur Modelle zur Bild-Markierung mittels Conditional Random Fields
ist f\"ur gew\"ohnlich nur approiximativ moeglich, bedingt d\"urch das
Vorhandensein von Kreisen in den zugrunde liegenden Nachbarschaftsgraphen.
Aus diesem Grund, und trotz der Beliebtheit von Conditional Random Field
Verfahren, ist das strukturierte Lernen f\"ur solche Anwendungen schlecht
verstanden.
%
Wir untersuchen verschiedene Lernalgorithmen in diesem
Zusammenhang. Wir zeigen, dass es m\"oglich ist trotz des Vorhandenseins von
Kreisen in den Nachbarschaftsgraphen exakte strukturierte Modelle zu lernen.
Wir stellen ausserdem eine Software-Bibliothek vor, die es erlaubt einen
weitreichenden Vergleich der besten Lernverfahren f\"ur strukturiertes Lernen
durchzuf\"uhren.
Unsere Studie erlaubt uns eine Charakterisation der betrachteten Algorithmen
in einer Reihe von Anwendungen, insbesondere der semantischen Segmentierung und
Objektklassensegmentierung.

@@

@@

\chapter{Conclusion and Future Direction}
Current progress in computer vision \dots at an incredible speed,
with new methods and applications emerging constantly.
Still, there are large differences in the paradigms employed by different researchers.
While it is generally aknowledged that context is one of the most important cues
in recognizing objects and interpreting scence, there is little consensus on how
contextual information should be modelled, or even learned.
The structured prediction paradigm allows a principled approach to incoporating
predictions within an image, and to include context information.
We investigated the potential of structural methods for the application of semantic image segmentation
and object recognition, appications to which structured methods have been applied successfully before.
We focus on \emph{learning} of structural models and the interaction of inference and learning
in the neighborhood models typically employed for semantic segmentation.
The thesis presents a software implementation of a variety of popular learning algorithms for structural
support vector machines, together with a thorough evaluation of their properties in the presence
of approximate inference.
We demonstated that exact learning is possible, even in the presence of loops in the
\dots factor graph. We also demonstrate the power of conditioning interactions
on data, learning spacial interactions in a RGB-D setting.

There are several directions for future research that we think would be interesting to pursue as an extention
of the presented results: 
\paragraph[Inference Machines]
Recently \citet{stoyanov2011empirical} started a new trend in structured
prediction, which is sometimes called ``inference machines''. The basic
principle is simple: view the process of prediction with a given inference
procedure as a prediction method and optimize parameters of this method using
empirical risk minimization.  The work of \citet{stoyanov2011empirical}, used
loopy belief propagation as their inference algorithm and the optimization is
carried out simply using gradient descent on the non-convex but differentiable
loss function.  Other recent work in this direction includes
\citet{krahenbuhlparameter}, who used mean-field inference in a fully connected
conditional random field and \citet{jancsarylearning}, who used closed form
inference in a Gaussian CRF\@.
While these algorithms show great promise, their relation to the traditional
approach of structured prediction used in this work is mostly unclear. In particular,
if exact traditional learning is possible in a model, it is unclear how much
can be gained by direct empirical risk minimization.
Little empirical comparision was performed, and we are not aware of theoretical
work in this direction, leaving much room for future investigation of this
direction.
\paragraph[Non-Linear Models]
In this work, we only considered models that are linear in the input features--though
features are highly non-linear in the original input pixels.
Kernelization of structural support vector machines is trivial in theory, but
had only limited success in the context of CRFs for image
segmentation~\citep{lucchi2012structured}.
Other

\paragraph[Latent Variable Models]
\paragraph[Feature Design]

%Vision is challenging
%context matters
%structured prediction allows modeling and learning of context and relations
%thesis gives insight into some relations of approximate inference and learning
%gives framework for evaluation
%comparison of methods

which low-level cues?
superpixels?
non-linear models?
latent variables?
inference engines
